A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-15 bioc-workflow.Rmd

```{r classify, eval=TRUE}
hl <- svmClassification(hl, params,
                        class.weights = w,
                        fcol = "markers")
```

@@

```{r setColors, include=FALSE}
setStockcol(NULL)
setStockcol(paste0(getStockcol(), 70))
par(mfrow = c(1, 1))
```
```{r plotSVM, eval=TRUE}
## set point size of each protein to be inversely proportional to the
ptsze <- exp(fData(hl)$svm.scores) - 1

>>>>

```{r classify}
hl <- svmClassification(hl, params,
                        class.weights = w,
                        fcol = "markers")
```

@@

```{r setColors, include=FALSE}
setStockcol(NULL)
setStockcol(paste0(getStockcol(), 70))
par(mfrow = c(1, 1))
```
```{r plotSVM}
## set point size of each protein to be inversely proportional to the
ptsze <- exp(fData(hl)$svm.scores) - 1
